Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 Experiments.tex
saved 4-5 lines and minor corrections.

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak1.pdf}
    \caption{Weak scalability: average pilot duration, average  duration of a
    single AthenaMP execution, and pilot's overhead as a function of different pilot sizes (200, 500, 1000 and 2000 nodes).}
\label{fig:weakScal1a}
\end{figure}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak2.pdf}
    \caption{Weak scalability with multiple generations: average pilot
    duration, average duration of five sequential AthenaMP executions, and
    pilot's overhead for different pilot sizes (256, 512, 1024 and 2048 nodes).}
\label{fig:weakScal2a}
\end{figure}

>>>>

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak1.pdf}
    \caption{Weak scalability: average pilot duration, average  duration of a
    single AthenaMP execution, and pilot's overhead as a function of pilot sizes (200, 500, 1000 and 2000 nodes).}
\label{fig:weakScal1a}
\end{figure}

@@

\begin{figure}[!htb]
        \includegraphics[height=4.5cm,width=\columnwidth]{./figures/NGE/weak2.pdf}
    \caption{Weak scalability with multiple generations: average pilot
    duration, average duration of five sequential AthenaMP executions, and
    pilot's overhead for pilot sizes (256, 512, 1024 and 2048 nodes).}
\label{fig:weakScal2a}
\end{figure}

### 2017-04-04 PandaOverview.tex
saved 4-5 lines and minor corrections.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_architecture.pdf}
    \caption{PanDA WMS architecture. Numbers indicates the execution process
    based on JEDI. Several subsystems and components, the architectural
    details of PanDA Pilot and the communication among subsystem's components
    are abstracted to improve clarity.}
\label{fig:architecture}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/panda_architecture.pdf}
    \caption{PanDA WMS architecture. Numbers indicates the execution process
    based on JEDI. Several subsystems and components, the architectural
    details of PanDA Pilot and the communication among components
    are abstracted for clarity.}
\label{fig:architecture}
\end{figure}
